Numerical Solution of Point Defect Equations by MOOSE

### 2020-12-02 examples/point_defects/article/article.tex
imperfect-article

%TC:ignore
\keywords{point defect equations, rate theory, radiation damage, MOOSE}
%TC:endignore

@@

\begin{table}[h!]
  \centering
  \caption{Material Properties for Nickel\cite{walgraef1996}}
  \label{table:1}
  \begin{tabular}{ ||p{2cm}|p{2cm}||  }
     % \hline
     % \multicolumn{5}{|c|}{Material Properties} \\
     \hline
     Property & Value\\
     \hline\hline
     a  & 0.352 nm\\
     V  & 0.01206 nm^3\\
     E_{m,i}  & 0.30 eV\\
     E_{m,v}  & 1.30 eV\\
     E_{f,i}  & 4.27 eV\\
     E_{f,v}  & 1.60 eV\\
     D_{0,i}  & 1e-7 m^2/s\\
     D_{0,v}  & 6e-5 m^2/s\\

@@

\begin{table}[h!]
  \centering
  \caption{Simulation Parameters}
  \label{table:2}
  \begin{tabular}{ ||p{2cm}|p{2cm}|p{4cm}|p{2cm}|p{2cm}||  }
     % \multicolumn{5}{|c|}{Simulation Parameters} \\
     \hline
     Type & Dose Rate & Defect Production Profile & Temperature & Sink Density\\
     \hline
     \hline
     Neutron  & 1e-3  & Uniform     & 773K & 1e18\\
              & 1e-6  & Uniform     & 773K & 1e18\\
     \hline
     Ion      & 1e-3  & Distributed & 773K & 1e18\\
              & 1e-6  & Distributed & 773K & 1e18\\
     \hline
  \end{tabular}
\end{table}

@@

The production bias is a factor that is used to create a difference between interstitial
and vacancy generation in domain. As the production bias increases, vacancy production
increases and the gap between steady state vacancy and interstitial concentrations gets wider.
Most of the plots in this part are generated by using the simulation results for Cs=1e18 m -3 ,
T=773K, K 0 =1e-3 dpa/s.

  \subsection{Neutron Irradiation}
    \subsubsection{Concentrations}
      \begin{figure}[h!]  %Neutron - 1e-6 dpa/s - %0 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-neutron-0}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-neutron-0}}
        \caption{Concentration profiles for 1e-6 dpa/s and 0\% Production Bias}
        \label{figure:1}
      \end{figure}
      \begin{figure}[h!]  %Neutron - 1e-3 dpa/s - %0 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-high_neutron-0}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-high_neutron-0}}
        \caption{Concentration profiles for 1e-3 dpa/s and 0\% Production Bias}
        \label{figure:2}
      \end{figure}
      \begin{figure}[h!]  %Neutron - 1e-6 dpa/s - %5 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-neutron-5}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-neutron-5}}
        \caption{Concentration profiles for 1e-6 dpa/s and 5\% Production Bias}
        \label{figure:3}
      \end{figure}
      \begin{figure}[h!]  %Neutron - 1e-3 dpa/s - %5 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-high_neutron-5}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-high_neutron-5}}
        \caption{Concentration profiles for 1e-3 dpa/s and 5\% Production Bias}
        \label{figure:4}
      \end{figure}
      \begin{figure}[h!]  %Neutron - 1e-3 dpa/s - %5 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{super_saturation_500-5000nm-neutron-5}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{super_saturation_500-5000nm-high_neutron-5}}
        \caption{Vacancy Supersaturation profiles for 1e-6 dpa/s and 1e-3 dpa/s with 5\% Production Bias}
        \label{figure:5}
      \end{figure}
    \subsubsection{Sink Strengths}
      \begin{figure}[h!]
        \centering
        \includegraphics[scale=0.6]{concentration_proflies_MOOSE_Analytical_Neutron_0}
        \caption{Comparison of MOOSE results with analytical solution for a 1D spherical grain.\cite{heald1977}}
        \label{figure:6}
      \end{figure}

  \subsection{Ion Irradiation}
    \subsubsection{Concentrations}
      \begin{figure}[h!]  %Ion - 1e-6 dpa/s - %0 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-ion-0}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-ion-0}}
        \caption{Concentration profiles for 1e-6 dpa/s and 0\% Production Bias}
        \label{figure:7}
      \end{figure}
      \begin{figure}[h!]  %Ion - 1e-3 dpa/s - %0 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-low_ion-0}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-low_ion-0}}
        \caption{Concentration profiles for 1e-3 dpa/s and 0\% Production Bias}
        \label{figure:8}
      \end{figure}
      \begin{figure}[h!]  %Ion - 1e-6 dpa/s - %5 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-ion-5}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-ion-5}}
        \caption{Concentration profiles for 1e-6 dpa/s and 5\% Production Bias}
        \label{figure:9}
      \end{figure}
      \begin{figure}[h!]  %Ion - 1e-3 dpa/s - %5 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-low_ion-5}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-low_ion-5}}
        \caption{Concentration profiles for 1e-3 dpa/s and 5\% Production Bias}
        \label{figure:10}
      \end{figure}
      \begin{figure}[h!]  %Neutron - 1e-3 dpa/s - %5 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{super_saturation_500-5000nm-ion-5}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{super_saturation_500-5000nm-low_ion-5}}
        \caption{Vacancy Supersaturation profiles for 1e-6 dpa/s and 1e-3 dpa/s with 5\% Production Bias}
        \label{figure:11}
      \end{figure}

    \subsubsection{Sink Strengths}

@@

>>>>

%TC:ignore
\keywords{point defect equations, rate theory, interstitial, vacancy, radiation damage, MOOSE}
%TC:endignore

@@

\begin{table}[h!]
  \centering
  \caption{Material Properties for Nickel\cite{walgraef1996}}
  \label{table:Ni_material_properties}
  \begin{tabular}{ ||p{2cm}|p{2cm}||  }
     % \hline
     % \multicolumn{5}{|c|}{Material Properties} \\
     \hline
     Property & Value\\
     \hline\hline
     a  & 0.352 nm\\
     V  & 0.01206 nm^3\\
     E_{m,i}  & 0.30 eV\\
     E_{m,v}  & 1.30 eV\\
     E_{f,i}  & 4.27 eV\\
     E_{f,v}  & 1.60 eV\\
     D_{0,i}  & 1e-7 m^2/s\\
     D_{0,v}  & 6e-5 m^2/s\\

@@

\begin{table}[h!]
  \centering
  \caption{Simulation Parameters}
  \label{table:simulation_parameters}
  \begin{tabular}{ ||p{2cm}|p{2cm}|p{3cm}|p{2cm}|p{2cm}||  }
     % \multicolumn{5}{|c|}{Simulation Parameters} \\
     \hline
     Type & Dose Rate & Defect Production & Temperature & Sink Density\\
     \hline
     \hline
     Neutron  & 1e-3 dpa/s  & Uniform     & 773 K & 1e18 1/m^{3}\\
              & 1e-6 dpa/s  & Uniform     & 773 K & 1e18 1/m^{3}\\
     \hline
     Ion      & 1e-3 dpa/s  & Distributed & 773 K & 1e18 1/m^{3}\\
              & 1e-6 dpa/s  & Distributed & 773 K & 1e18 1/m^{3}\\
     \hline
  \end{tabular}
\end{table}

!!!mention!!! The production bias is a factor that is used to create a difference between interstitial
and vacancy generation in domain.}

@@

The simulation results for different irradiation types are presented by defect concentration, vacancy supersaturation as well as sink strength plots. The calculated sink strengths are also tabulated for different domain size and bias rates.

  \subsection{Neutron Irradiation}
    \subsubsection{Concentrations} \hspace{10pt}
      \begin{figure}[h!]  %Neutron - 1e-6 dpa/s - %0 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-neutron-0}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-neutron-0}}
        \caption{Concentration profiles for neutron irradation with 0\% Production Bias}
        \label{figure:concentrations_neutron_0_1e-6}
      \end{figure}
      \begin{figure}[h!]  %Neutron - 1e-3 dpa/s - %0 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-high_neutron-0}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-high_neutron-0}}
        \caption{Concentration profiles for high dose neutron irradation with 0\% Production Bias}
        \label{figure:concentrations_neutron_0_1e-3}
      \end{figure}
      \begin{figure}[h!]  %Neutron - 1e-6 dpa/s - %5 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-neutron-5}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-neutron-5}}
        \caption{Concentration profiles for neutron irradation with 5\% Production Bias}
        \label{figure:concentrations_neutron_5_1e-6}
      \end{figure}
      \begin{figure}[h!]  %Neutron - 1e-3 dpa/s - %5 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-high_neutron-5}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-high_neutron-5}}
        \caption{Concentration profiles for high dose neutron irradation with 5\% Production Bias}
        \label{figure:concentrations_neutron_5_1e-3}
      \end{figure}
      \begin{figure}[h!]  %Nuetron - Vacancy Supersaturation - 5% Bias
        \centering
        \subfloat{\includegraphics[scale=0.6]{super_saturation_500-5000nm-neutron-5}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{super_saturation_500-5000nm-high_neutron-5}}
        \caption{Vacancy Supersaturation profiles for normal and high dose neutron irradation with 5\% Production Bias}
        \label{figure:vacancy_supersaturation_neutron_5}
      \end{figure}
    \subsubsection{Sink Strengths}
    The grain boundary sink strengths are calculated by using the equation \ref{equation:sink_strength}. First of all the defect concentration profile found by MOOSE is validated by comparing to analytical result as shown in Fig.\ref{figure:concentrations_MOOSE_analytical}
      \begin{figure}[h!]
        \centering
        \includegraphics[scale=0.6]{concentration_profiles_MOOSE_Analytical_Neutron_0}
        \caption{Comparison of MOOSE results with analytical solution for a 1D spherical grain.\cite{heald1977}}
        \label{figure:concentrations_MOOSE_analytical}
      \end{figure}
      \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s - 0% Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{sink_strength_moose_neutron_0_k}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{sink_strength_moose_neutron_0_Z}}
        \caption{Sink Strengths for neutron irradiation with 0\% Production Bias}
        \label{figure:sink_strengths_neutron_0_1e-6}
      \end{figure}
      \begin{figure}[h!]  %Sink Strength - Neutron 1e-6 dpa/s - 5% Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{sink_strength_moose_neutron_5_k}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{sink_strength_moose_neutron_5_Z}}
        \caption{Sink Strengths for neutron irradation with 5\% Production Bias}
        \label{figure:sink_strengths_neutron_5_1e-6}
      \end{figure}

  \subsection{Ion Irradiation}
    \subsubsection{Concentrations}
      \begin{figure}[h!]  %Ion - 1e-3 dpa/s - %0 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-ion-0}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-ion-0}}
        \caption{Concentration profiles for low dose ion irradation with 0\% Production Bias}
        \label{figure:concentrations_ion_0_1e-6}
      \end{figure}
      \begin{figure}[h!]  %Ion - 1e-6 dpa/s - %0 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-low_ion-0}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-low_ion-0}}
        \caption{Concentration profiles for ion irradiation with 0\% Production Bias}
        \label{figure:concentrations_ion_0_1e-3}
      \end{figure}
      \begin{figure}[h!]  %Ion - 1e-3 dpa/s - %5 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-ion-5}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-ion-5}}
        \caption{Concentration profiles for low dose ion irradation with 5\% Production Bias}
        \label{figure:concentrations_ion_5_1e-6}
      \end{figure}
      \begin{figure}[h!]  %Ion - 1e-6 dpa/s - %5 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{interstitial_concentration_500-5000nm-low_ion-5}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{vacancy_concentration_500-5000nm-low_ion-5}}
        \caption{Concentration profiles for ion irradation with 5\% Production Bias}
        \label{figure:concentrations_ion_5_1e-3}
      \end{figure}
      \begin{figure}[h!]  %Ion - %5 Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{super_saturation_500-5000nm-ion-5}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{super_saturation_500-5000nm-low_ion-5}}
        \caption{Vacancy Supersaturation profiles for low dose and ion irradation with 5\% Production Bias}
        \label{figure:vacancy_supersaturation_ion_5}
      \end{figure}

    \subsubsection{Sink Strengths}
      \begin{figure}[h!]  %Sink Strength - ion 1e-3 dpa/s - 0% Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{sink_strength_moose_ion_0_k}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{sink_strength_moose_ion_0_Z}}
        \caption{Sink Strengths for low dose ion irradation with 0\% Production Bias}
        \label{figure:sink_strengths_ion_0_1e-6}
      \end{figure}
      \begin{figure}[h!]  %Sink Strength - ion 1e-3 dpa/s - 5% Bias rate
        \centering
        \subfloat{\includegraphics[scale=0.6]{sink_strength_moose_ion_5_k}}
        \qquad
        \subfloat{\includegraphics[scale=0.6]{sink_strength_moose_ion_5_Z}}
        \caption{Sink Strengths for ion irradiation with 5\% Production Bias}
        \label{figure:sink_strengths_ion_5_1e-6}
      \end{figure}

@@

The most significant parameters are found as domain size and bias rate as shown in plots in this section.
